---
title: "lab_report_knapsack"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette:
  toc: true
vignette: >
  %\VignetteIndexEntry{AdvancedRlab6}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AdvancedRlab6)
```

# The Knapsack Problem

## Description

The knapsack problem is a discrete optimization problem where we have a knapsack that can take a limited weight W and we want to fill this knapsack with a number of items i = 1, ..., n, each with a weight w_i and a value v_i. The goal is to find the knapsack with the largest value of the elements added
to the knapsack. 

In this package, we have implemented the Brute Force algorithm, the Dynamic algorithm and the Heuristic Greedy algorithm as described in pseudo-code on Wikipedia's page <https://en.wikipedia.org/wiki/Knapsack_problem>. We have also tried *parallelizing* in the Brute Force algorithm using Hadley's instructions (Found here: <http://adv-r.had.co.nz/Profiling.html>).

The data set used for testing the algorithms can be seen below:

```{r}
set.seed(42)
n <- 100000
knapsack_objects <- data.frame(w = sample(1:4000, size = n, replace = TRUE), v = runif(n = n, 0, 10000))
```

## Brute Force algorithm

Example (using $n = 16$):

```{r}
AdvancedRlab6::brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)
```

How much time does it takes to run the algorithm for $n = 16$ objects?

```{r}
ptm <- proc.time()  
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)
t1 <- proc.time() 
t2 <- (t1-ptm)[3]
```

The `brute_force_knapsack()` takes ~`r t2`seconds for $n = 16$.

## Parallelizing Brute Force algorithm

Example (using $n = 50$):

```{r}
AdvancedRlab6::brute_force_knapsack(x = knapsack_objects[1:50,], W = 3500, TRUE)
```

```{r, eval = FALSE}
ptm <- proc.time()  
brute_force_knapsack(x = knapsack_objects[1:50,], W = 3500, TRUE)
t1 <- proc.time() 
t2 <- (t1-ptm)[3]
```


```{r, eval = FALSE}
ptm <- proc.time()  
brute_force_knapsack(x = knapsack_objects[1:50,], W = 3500, FALSE)
t1 <- proc.time() 
t2 <- (t1-ptm)[3]
```

For $n = 50$ the `brute_force_knapsack()` with `parallel = TRUE` takes ~ seconds.

For $n = 50$ the `brute_force_knapsack()` with `parallel = FALSE` takes ~ seconds.

## Dynamic algorithm

Example (using $n = 500$):

```{r}
AdvancedRlab6::knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500)
```

How much time does it takes to run the algorithm for $n = 500$ objects?

```{r}
ptm <- proc.time()  
knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500)
t1 <- proc.time() 
t2 <- (t1-ptm)[3]
```

The `knapsack_dynamic()` takes ~`r t2`seconds for $n = 500$.

## Heuristic Greedy algorithm

Example (using $n = 1000000$):

```{r}
AdvancedRlab6::greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500)
```

How much time does it takes to run the algorithm for $n = 1000000$ objects?

```{r}
ptm <- proc.time()  
greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500)
t1 <- proc.time() 
t2 <- (t1-ptm)[3]
```

The `greedy_knapsack()` takes ~`r t2`seconds for $n = 1000000$.

## Profiling and optimizing code
